---
title: "encode_deal"
author: "Li Yuan"
date: "7/13/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r, message=FALSE}
library(readtext)
library(antiword)
library(tidyverse)
library(ggplot2)
library(textreadr)
library(stringi)
library(textclean)
library(SemNetCleaner)
library(readxl)
```


# Load data

```{r}
deal <- read_csv("deal(1).csv", col_types = cols(.default = "c")) %>% select(`Deal name`, `Signing date`, `Closing date`)
View(deal)

merge_deal_lawyer <- read_csv("merge_deal_lawyer.csv")
View(merge_deal_lawyer)

distin_com_lawyer <- read_csv("distinct_binded_lawyer_2020.csv", 
    col_types = cols(FirmId = col_character(), 
        `JD Year` = col_character(), ProbabilityOfMove = col_character(), 
        Notes = col_character()))
View(distin_com_lawyer)
```

# encode the deal into number

```{r}
mapping_index <- deal %>%
  mutate(Deal_number := 1:n()) %>% 
  select(Deal_number, `Deal name`) %>%
  rename(Deal_name = `Deal name`)
View(mapping_index)
write_csv(x = mapping_index, file = "map_index.csv")
```

# Match these new encoded to deal_lawyer_data

```{r}
encoded_merge_dl <- merge_deal_lawyer %>%
  left_join(mapping_index, by = c("deal" = "Deal_name")) %>%
  select(Deal_number, everything(), -deal) 
View(encoded_merge_dl)
```

```{r}
encoded_deal <- deal %>%
  left_join(mapping_index, by = c("Deal name" = "Deal_name"))
View(encoded_deal)
```

# Only keep duplicate lawyer in M&A

```{r}
new_distinct_com <- distin_com_lawyer %>%
  distinct(Last, First, `JD Year`, `Law School`, Undergrad, Gender, Race, .keep_all = T)
View(new_distinct_com)
write_csv(x = new_distinct_com, file = "keep_MA_first.csv")
```

# merge using distin_com_lawyer

## First confidence

```{r}
deal_lawyer_full <- encoded_merge_dl %>%
  mutate(First = tolower(gsub("\\.$", "", First)), 
         Last = tolower(gsub("\\.$", "", Last)), 
         Firm = tolower(gsub("\\.$", "", Law_Firm))) %>%
  inner_join(new_distinct_com %>% mutate(Firm = tolower(gsub("\\.$", "", Firm)), 
                                          First = tolower(gsub("\\.$", "", First)), 
                                          Last = tolower(gsub("\\.$", "", Last))), 
            by = c("Firm" = "Firm", "First" = "First", "Last" = "Last")) %>% 
  mutate(First = str_to_title(First), Last = str_to_title(Last)) #%>%
  #select(-Firm)


deal_lawyer_full <- deal_lawyer_full %>%
  left_join(encoded_deal, by = c("Deal_number" = "Deal_number")) %>%
  select(Deal_number, `Signing date`, `Closing date`, everything())

View(deal_lawyer_full)

write_csv(x = deal_lawyer_full, file = "com_deal_lawyer_full.csv")
```

### Anti-join to get rows which are not matched with any rows in y

```{r}
deal_lawyer_full_no_match <- encoded_merge_dl %>%
  mutate(First = tolower(gsub("\\.$", "", First)), 
         Last = tolower(gsub("\\.$", "", Last)), 
         Firm = tolower(gsub("\\.$", "", Law_Firm))) %>%
  anti_join(new_distinct_com %>% mutate(Firm = tolower(gsub("\\.$", "", Firm)), 
                                         First = tolower(gsub("\\.$", "", First)), 
                                         Last = tolower(gsub("\\.$", "", Last))), 
            by = c("Firm" = "Firm", "First" = "First", "Last" = "Last")) %>% 
  mutate(First = str_to_title(First), Last = str_to_title(Last)) %>%
  select(-Firm)


deal_lawyer_full_no_match <- deal_lawyer_full_no_match %>%
  left_join(encoded_deal, by = c("Deal_number" = "Deal_number")) %>%
  select(Deal_number, `Signing date`, `Closing date`, everything())

 #View(deal_lawyer_full_no_match)

write_csv(x = deal_lawyer_full_no_match, file = "com_deal_lawyer_full_no_match.csv")
```

## Second confidence on no match data using first and last name

```{r}
deal_lawyer_first_last <- deal_lawyer_full_no_match %>%
  mutate(First = tolower(gsub("\\.$", "", First)), 
         Last = tolower(gsub("\\.$", "", Last))) %>%
  inner_join(new_distinct_com %>% mutate(First = tolower(gsub("\\.$", "", First)), 
                                          Last = tolower(gsub("\\.$", "", Last))), 
            by = c("First" = "First", "Last" = "Last")) %>% 
  mutate(First = str_to_title(First), Last = str_to_title(Last))


View(deal_lawyer_first_last)

write_csv(x = deal_lawyer_first_last, file = "com_deal_lawyer_first_last.csv")
```

## Anti-join to get no match

```{r}
deal_lawyer_first_last_no_match <- deal_lawyer_full_no_match %>%
  mutate(First = tolower(gsub("\\.$", "", First)), 
         Last = tolower(gsub("\\.$", "", Last))) %>%
  anti_join(new_distinct_com %>% mutate(First = tolower(gsub("\\.$", "", First)), 
                                         Last = tolower(gsub("\\.$", "", Last))), 
            by = c("First" = "First", "Last" = "Last")) %>% 
  mutate(First = str_to_title(First), Last = str_to_title(Last))


#View(deal_lawyer_first_last_no_match)

write_csv(x = deal_lawyer_first_last_no_match, file = "com_deal_lawyer_first_last_no_match.csv")
```

# The thrid confidence

```{r}
deal_lawyer_firm_last <- deal_lawyer_first_last_no_match %>%
  mutate(Firm = tolower(gsub("\\.$", "", Law_Firm)), 
         Last = tolower(gsub("\\.$", "", Last))) %>%
  inner_join(new_distinct_com %>% mutate(Firm = tolower(gsub("\\.$", "", Firm)), 
                                          Last = tolower(gsub("\\.$", "", Last))), 
            by = c("Firm" = "Firm", "Last" = "Last")) %>% 
  mutate(Last = str_to_title(Last)) %>%
  select(-First.y) %>%
  rename(First = First.x)

View(deal_lawyer_firm_last)

write_csv(x = deal_lawyer_firm_last, file = "com_deal_lawyer_firm_last.csv")
```

## Anti-join to get remaining unmatched rows

```{r}
deal_lawyer_firm_last_no_match <- deal_lawyer_first_last_no_match %>%
  mutate(Firm = tolower(gsub("\\.$", "", Law_Firm)), 
         Last = tolower(gsub("\\.$", "", Last))) %>%
  anti_join(new_distinct_com %>% mutate(Firm = tolower(gsub("\\.$", "", Firm)), 
                                         Last = tolower(gsub("\\.$", "", Last))), 
            by = c("Firm" = "Firm", "Last" = "Last")) %>% 
  mutate(Last = str_to_title(Last)) %>%
  select(-Firm)

# View(deal_lawyer_firm_last_no_match)

write_csv(x = deal_lawyer_firm_last_no_match, file = "com_deal_lawyer_firm_last_no_match.csv")
View(deal_lawyer_firm_last_no_match)
```

# Find duplicates from first and last match

```{r}
dupli_first_last <- deal_lawyer_first_last %>%
  count(Deal_number, First, Last) %>%
  filter(n > 1) %>%
  arrange(desc(n))

dupli_first_last <- deal_lawyer_first_last %>%
  inner_join(dupli_first_last, by = c("Deal_number" = "Deal_number", "First" = "First", "Last" = "Last")) %>%
  select(Deal_number, `Signing date`, `Closing date`, First, MI.x, Last, n, everything()) 

write_csv(x = dupli_first_last, file = "duplicate_first_last.csv")
View(dupli_first_last)
```


# Find duplicates from firm and last match

```{r}
dupli_firm_last <- deal_lawyer_firm_last %>%
  count(Deal_number, Law_Firm, Last) %>%
  filter(n > 1) %>%
  arrange(desc(n))

dupli_firm_last <- deal_lawyer_firm_last %>%
  inner_join(dupli_firm_last, by = c("Deal_number" = "Deal_number", "Law_Firm" = "Law_Firm", "Last" = "Last")) %>%
  select(Deal_number, `Signing date`, `Closing date`, First, MI.x, Last, n, everything()) 

write_csv(x = dupli_firm_last, file = "duplicate_firm_last.csv")
View(dupli_firm_last)
```

# Stack all three matched dataset

```{r}
col_full <- colnames(deal_lawyer_full)
col_fl <- colnames(deal_lawyer_first_last)
col_lf <- colnames(deal_lawyer_firm_last)
```

```{r}
length(col_full)
length(col_fl)
length(col_lf)
```

```{r}
setdiff(col_fl, col_full)
setdiff(col_full, col_fl)
```

```{r}
one_two_three <- rbind(deal_lawyer_full, deal_lawyer_first_last, deal_lawyer_firm_last)
View(one_two_three)
write_csv(x = one_two_three, file = "three_matched_stacked.csv")
```

